---
output:
  github_document:
    html_preview: FALSE
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, error = FALSE)
```

# simpipe2docker links Docker containers and R environment and performs simulations for single-cell and spatial transcriptomics data.

## Installation

### simpipe2docker

You can install the development version of simpipe from [GitHub](https://github.com/) with:

```{r install, eval=FALSE}
# install.packages("devtools")
devtools::install_github("duohongrui/simpipe2docker")
```

### Docker

Firstly, users should install the the Docker Desktop (https://www.docker.com/).

After installing Docker Desktop and starting the service, please check it by:

```{r check_docker}
simpipe2docker::test_docker_installation(detailed = TRUE)
```

Next, pull our Docker image called [simpipe](https://hub.docker.com/repository/docker/duohongrui/simpipe/general):

Terminal command:

```{bash pull_images1, eval=FALSE}
docker pull duohongrui/simpipe:latest
```

Or you can run command in R:

```{r pull_images2, eval=FALSE}
babelwhale::pull_container(container_id = "duohongrui/simpipe:latest")
```

Now, you have already installed Docker Desktio successfully!


## Usage

The documents of estimating parameters from real data and simulating new datasets by **simpipe2docker** are all described on our [simsite](http://www.ciblab.net/software/Simsite/).


## Contact

If you have any question, please email to Hongrui Duo (duohongrui@cqnu.edu.cn) or raise an issue for that.

